Fractional Types

### 2016-12-19 typespp.tex
small tweak

Compact closed categories support various interesting
constructions~\cite{abramsky-2008}, such as duals, name and coname, and
trace~\cite{joyal1996traced,Hasegawa:1997:RCS:645893.671607}, which eventually
lead to a certain notion of recursive higher-order functions. These
constructions do not immediately transfer to the context of $\Pi^/$ as we have
explicit quantifiers and synchronization primitives that are not present in the
conventional setting. Resolving these subtleties will provide the first
operational interpretation known to us of multiplicative higher-order recursive
functions.

>>>>

Compact closed categories support various interesting
constructions~\cite{abramsky-2008}, such as duals, name and coname, and
trace~\cite{joyal1996traced,Hasegawa:1997:RCS:645893.671607}, which eventually
lead to a certain notion of recursive higher-order functions. These
constructions do not immediately transfer to the context of $\Pi^/$ as we have
pointed types with explicit quantifiers and synchronization primitives that are
not present in the conventional setting. Adapting the conventional constructions
requires resolving some subtleties and will provide the first operational
interpretation known to us of multiplicative higher-order recursive functions.
